Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-01 Paper.Rmd
fix notations

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.25
fontfamily: times
---

@@

# Introduction

@@

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Since OCR don't share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this study, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].

@@

Many independent variables and their relationship between perceived helpfulness were examined by researchers. @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group try to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is heavily dependent on the data itself. In my paper, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.

@@

The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015]. These metrics can measure the sentiment of the review itself. They are usually different than Review Extremity. In most cases Review Extremity and Review Sentiment (Valence) don't match [@zhang2011]. @baek2012 and @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness. The relationship between the proportion of positive words and perceived helpfulness was found to be negative [@kuan2015].

@@

Any website which offers online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon was used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after the consumption. Though, Credence goods won't be discussed any further in this study.

@@

Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones. Someone else's hair in one's meal has the potential of ruining the whole meal. On the contrary a plate of hair won't turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair. @rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects. Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative Differentiation [@rozin2001; @sen2007; @eslami2018]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].

**Negative Potency** defends that the exact opposite of something positive carries heavier weight. In other words, negative events are much more impactful than their exact positive counterparts. For instance, losing 100\$ could have a harder psychological effect on a person than that particular person is gaining 100\$. Loss Aversion [@kahneman1979; @tversky1991] is the phenomenon where the Negative Potency can be observed the best. People risk more/less when they are losing/gaining something. This behavior can be explained by the Endowment Effect [@kahneman1990]. Endowment effect occurs because people usually over-estimate the value of their belongings, for example a pencil. However, they would have under-valued the same pencil if the item didn't belong to them. The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquiring the same pencil.

**Greater Steepness of Negative Gradients** simply implies that the marginal psychological effect of a negative entity is much more higher than a positive one. In other words, negative things cause more negativity as the time goes on.

**Negativity Dominance** asserts that a balanced mixture of positive and negative evaluations creates a perception of negativity. This means that negative entities have higher weight than positive entities. This is apparent in religions. For most of the religions being a good and pious person takes time, demands utmost care. However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 [@python3]. The scraper got the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

From IMDB reviews of 22 movies were collected as experience goods. In total, 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five. In other words, reviews that had less than 5 Total Votes were removed from the analysis data [@choi2020; @baek2012]. At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times. Most of the search product reviews aren't getting voted and even possible that they aren't getting read at all. This might support the idea that people form more homogeneous opinions about search goods [@hong2014]. Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information. On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times. This might be because people form heterogeneous opinions about experience goods [@hong2014].

@@

Exploratory Data Analysis(EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value. I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.

The goal of this section is not "confirmatory" whatsoever. Both dependent and independent variables are going to be introduced with an emphasis on their quantitative features such as their distributions and potential transformations which can be applied to the variables in question. In addition to this, bivariate relations between independent and dependent variables will be plotted in order to get an initial idea about the potential effects along with similar findings from the literature. Thus, in a sense, EDA in this section doesn't carry out the purpose of discovery, rather it merely puts the data on the spot for the sake of transparency.

@@

search_goods %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = NULL)

@@

As it can be seen the distribution is rather skewed. Looks like in the electronics case, readers find some reviews very helpful. In fact, in the data there is one review which had over 170 helpful votes with zero unhelpful votes. On the other hand, distribution for experience goods on Figure \@ref(fig:IV-Hist-Exp) presents a different picture. This time helpfulness ratio is sort of normally distributed. There aren't very helpful reviews. The most helpful review interval seems to be lying between 70% to 80%.

On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard error will be calculated correctly or not in a regression method. @li2012 found out that given a relatively high sample size (\>3000) linear regression techniques produces sound estimates of coefficients. Since the sample size for search goods is over 8000 it might be assumed that the use of linear regression methods is acceptable.

@@

@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

On Figure \@ref(fig:Search-Rating) (B) and Figure \@ref(fig:Experience-Rating) (B) the bivariate relationship between perceived helpfulness and review extremity can be seen. Again, as a researcher, I must emphasize that this analysis is not confirmatory. On figures, we can observe "U" type of relationship for both Search and Experience goods, though the non-linearity seems to be stronger with Search goods. This might suggest that on the average extreme reviews might be more helpful than moderate reviews [@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. On the other hand, it is observable that positive reviews on the average are more helpful than the rest. This might indicate that there is a linear positive relationship [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020].

@@

The exponential distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).

@@

1.  The first review date for a particular brand and model of a product (Movie, Phone, Laptop, TV) was taken.
2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
3.  Bigger numbers represent more recent reviews.

@@

On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen. On plots, x-axis labels were given in the logarithm of base 10 so 1.00 on the x-axis implies that 10% of the review was negative words. It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods don't have any negative words in them. For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.

@@

This variable was engineered in the same manner with its negative words counterpart. In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words. `r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods don't have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods. Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).

@@

On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts. Furthermore, these plots kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)). In a sense, both negative and positive proportions imply number of words. As the proportion increases so does the number of words. That's why aforementioned figures show similar relationships between variables. On higher dimensions these relationships might be different. That is why Exploratory Data Analysis should never be conducted in a confirmatory sense.

@@

"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].

@@

Before progressing to the modelling section, it would be a good practice to check the correlations between independent and control variables in order not to cause any multi-colinearity problems. As it can be seen on Figure \@ref(fig:Correlations) there aren't any major correlations between independent and control variables for both good types.

The relatively high positive/negative correlation between the Review Rating and Positive/Negative word proportions might give a hint about the usefulness of the lexicon. As the Review Rating gets higher the review contains more positive words and, on the other hand, low rated reviews have more negative words in them. This makes sense intuitively.

@@

@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal that there are some inherent problems with the particular product, making the feedback more helpful. On the other hand, for Experience Goods and in the specific case of movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989]. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

In order to decrease the uncertainty, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

So far it should be understood that people try to cut down their losses. That is why negative cues draw more attention than positive ones [@kahneman1979; @schindler2017]. Additionally, people find negative information more credible and persuasive than positive information [@ito1998; @Kanouse1984ExplainingNB]. It is known that Review Rating is the satisfaction level of a customer towards a product. However, Review Rating itself isn't enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product. The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review. Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments. Since in this study movies and electronics are compared, it is costlier to make a wrong decision on Search Goods than Experience Goods. Therefore, it is hypothesized that:

@@

Tobit model is also named as Censored Regression model. Censored data arises when there exist lower (censored from below) or upper (censored from above) or both lower and upper boundaries for the dependent variable. This type of data is fairly prevalent in Economics. For instance, in consumer economics there is no such thing as "negative consumption" or in labor economics there is no such thing as "negative work hours". Furthermore, there might be cases where some really high values could be recorded as "50,000 or more" because of the data collection design. Ordinary Least Squares can't take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.

@@

The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970. It shouldn't be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products. Electronics such as laptops or phones carry very strong search attributes whereas movies can be classified as "pure experience" goods which can be considered as a special case [@liu2014].

>>>>

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.5
fontfamily: times
---

@@

# Introduction {.unnumbered}

@@

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this study, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].

@@

Many independent variables and their relationship between perceived helpfulness were examined by researchers. @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group try to understand the relationship between reviewer status (reviewer expertise, number of past reviews etc.) and perceived helpfulness. [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is heavily dependent on the data itself. In my paper, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.

@@

The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015]. These metrics can measure the sentiment of the review itself. They are usually different than Review Extremity. In most cases Review Extremity and Review Sentiment (Valence) do not match [@zhang2011]. @baek2012 and @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness. The relationship between the proportion of positive words and perceived helpfulness was found to be negative [@kuan2015].

@@

Any website which offer online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data either from websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data. They have their respective APIs and on top of that, it is relatively easier to scrape both websites. Additionally, both websites offer product reviews for a numerous different types of products. Amazon is a huge e-retailer and offers a wide range of items. IMDB is a home for both critic and user reviews of Movies and TV Shows. In some other studies local equivalents of Amazon were used as well. [@sun2019]. @cao2011 used data from CNET Download.com which is a software distributor.

@@

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can not evaluate the good even after the consumption. Though, Credence goods will not be discussed any further in this study.

@@

Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones. Someone else's hair in one's meal has the potential of ruining the whole meal. On the contrary a plate of hair will not turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair. @rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects. Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative Differentiation [@rozin2001; @sen2007; @eslami2018]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].

**Negative Potency** defends that the exact opposite of something positive carries heavier weight. In other words, negative events are much more impactful than their exact positive counterparts. For instance, losing 100\$ could have a harder psychological effect on a person than that particular person is gaining 100\$. Loss Aversion [@kahneman1979; @tversky1991] is the phenomenon where the Negative Potency can be observed the best. People risk more (less) when they are losing (gaining) something. This behavior can be explained by the Endowment Effect [@kahneman1990]. Endowment effect occurs because people usually over-estimate the value of their belongings, for example a pencil. However, they would have under-valued the same pencil if the item did not belong to them. The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquiring the same pencil.

**Greater Steepness of Negative Gradients** simply implies that the marginal psychological effect of a negative entity is much more higher than a positive one. In other words, negative things cause more negativity as the time goes on. At the very least, the effects of negativeness are a lot more long-standing than effects of positiveness.

**Negativity Dominance** asserts that a balanced mixture of positive and negative evaluations creates a perception of negativity. This means that negative entities have higher weight than positive entities. This is apparent in religions. For the most of the religions being a good and pious person takes time, demands utmost care. However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3]. The scraper got the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

From IMDB reviews of 22 movies were collected as experience goods. In total, 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never got voted and probably they were never read because they got lost in the crowd of other reviews. To make sure that the analysis sample contains only the reviews which were actually read by potential buyers, a threshold of 5 was set for Total Votes. In other words, reviews that had less than 5 Total Votes were removed from the analysis data [@choi2020; @baek2012]. At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times. Most of the search product reviews are not getting voted and even possible that they are not getting read at all. This might support the idea that people form more homogeneous opinions about search goods [@hong2014]. Once a helpful review is written most of the other reviews become redundant since other reviews most likely convey similar information. On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times. This might be because people form heterogeneous opinions about experience goods [@hong2014].

@@

Exploratory Data Analysis (EDA) has no set of procedures to be followed. The way EDA is conducted almost always depends on the context of the research. @jebb2017 discusses that EDA encourages scientific replication if done properly. As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value. I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.

The goal of this section is not "confirmatory" whatsoever. Both dependent and independent variables are going to be introduced with an emphasis on their quantitative features such as their distributions and potential transformations which can be applied to the variables in question. In addition to this, bivariate relations between independent and dependent variables will be plotted in order to get an initial idea about the potential effects along with similar findings from the literature. Thus, in a sense, EDA in this section does not carry out the purpose of discovery, rather it merely puts the data on the spot for the sake of transparency.

@@

search_goods %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")

@@

As it can be seen the distribution is rather skewed. Looks like in the electronics case, readers find some reviews very helpful. In fact, in the data there is one review which had over 170 helpful votes with zero unhelpful votes. On the other hand, distribution for experience goods on Figure \@ref(fig:IV-Hist-Exp) presents a different picture. This time helpfulness ratio is sort of normally distributed. There are not very helpful reviews. The most helpful review interval seems to be lying between 70% to 80%.

On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard errors will be calculated correctly or not in a regression method. @li2012 found out that given a relatively high sample size (\>3000) linear regression techniques produces sound estimates of coefficients. Since the sample size for search goods is over 8000 it might be assumed that the use of linear regression methods is acceptable.

@@

@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

On Figure \@ref(fig:Search-Rating) (B) and Figure \@ref(fig:Experience-Rating) (B) the bivariate relationship between perceived helpfulness and review extremity can be seen. Once again, it must be emphasized that this analysis is not confirmatory. On figures, we can observe "U" type of relationship for both Search and Experience goods, though the non-linearity seems to be stronger with Search goods. This might suggest that on the average extreme reviews might be more helpful than moderate reviews [@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. On the other hand, it is observable that positive reviews on the average are more helpful than the rest. This might indicate that there is a linear positive relationship [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020].

@@

The exponential-like distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).

@@

1.  The first review date for a particular brand and model of a product (Movie, Phone, Laptop, TV) was taken.
2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and the model resulting an integer variable representing days.
3.  Bigger numbers represent more recent reviews.

@@

On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen. On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words. It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods do not have any negative words in them. For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.

@@

This variable was engineered in the same manner with its negative words counterpart. In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words. `r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods do not have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods. Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).

@@

On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts. Furthermore, these plots kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)). In a sense, both negative and positive proportions imply number of words. As the proportion increases so does the number of words. That is why aforementioned figures show similar relationships between variables. On higher dimensions these relationships might be different. That is why Exploratory Data Analysis should never be conducted in a confirmatory sense.

@@

Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].

@@

Before progressing to the modelling section, it would be a good practice to check the correlations between independent and control variables in order not to cause any multi-colinearity problems. As it can be seen on Figure \@ref(fig:Correlations) there are not any major correlations between independent and control variables for both good types.

The relatively high positive / negative correlation between the Review Rating and Positive / Negative word proportions might give a hint about the usefulness of the lexicon. As the Review Rating gets higher the review contains more positive words and, on the other hand, low rated reviews have more negative words in them. This makes sense intuitively.

@@

@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can not be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal that there are some inherent problems with the particular product, making the feedback more helpful. On the other hand, for Experience Goods and in the specific case of movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations are not impactful on the decision making process [@hoch1989]. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

In order to decrease the uncertainty in the most optimal way, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length. After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. This might decrease the average responsivess of the Perceived Helpfulness to the Review Length. However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

So far it should be understood that people try to cut down their losses. That is why negative cues draw more attention than positive ones [@kahneman1979; @schindler2017]. Additionally, people find negative information more credible and persuasive than positive information [@ito1998; @Kanouse1984ExplainingNB]. It is known that Review Rating is the satisfaction level of a customer towards a product. However, Review Rating itself is not enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product. The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review. Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments. Since in this study movies and electronics are compared, it is costlier to make a wrong decision on Search Goods than Experience Goods. Therefore, it is hypothesized that:

@@

Tobit model is also named as Censored Regression model. Censored data arises when there exist lower (censored from below) or upper (censored from above) or both lower and upper boundaries for the dependent variable. This type of data is fairly prevalent in economics. For instance, in consumer economics there is no such thing as "negative consumption" or in labor economics there is no such thing as "negative work hours". Furthermore, there might be cases where some really high values could be recorded as "50,000 or more" because of the data collection design. Ordinary Least Squares can not take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.

@@

The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970. It should not be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products. Electronics such as laptops or phones carry very strong search attributes whereas movies can be classified as "pure experience" goods which can be considered as a special case [@liu2014].
